|

### 2019-01-03 Paper 2019.Rmd
Minor cleanup

```{r Barber summary statistics fail, results="asis", eval=TRUE}
# This is what fails to knit (see error below)
stargazer(as.data.frame(subset(BarberNAs[,3:6])), digits=0, type="latex", title="Descriptive Statistics for State Level Campaign Finance Limits (n=1150 state-years)", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"), header=F)
```

@@

```{r CRI summary, results="asis", eval=T}
stargazer(as.data.frame(subset(corruption[,c(3,6)])), type="latex", digits=2, title="Descriptive Statistics for Corruption and Reflections", covariate.labels = c("Corruption Convictions Index (CCI)","Corruption Reflections Index (CRI)"), header=F)

@@

The fourth data set provides controls for the panel model. In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization (see Appendix A). Alt and Lassen's data set runs from 1976-2004. When included in the second and third models, this limits the analysis to the years from 1990-2004.

@@

```{r Empty, Binomial, and Poisson models}
# First, trying to run the model above but with the pglm() package
# pglm(formula, data, subset, na.action, effect = c("individual", "time", "twoways"), model = c("random", "pooling", "within", "between"), family, other = NULL, index = NULL, start = NULL, R = 20, ...)

@@

```{r CCI output to table}
stargazer(cci.base.pooled, 
          cci.limits.pooled, 
          cci.limits.fixed,
          cci.limits.fixed.time, 
          type="text",
          title = "Table 1: Are the presence or amounts of campaign limits correlated with corruption convictions?",
          out="collateral/CCI.htm",
          dep.var.labels = "Corruption Convictions Index",
          covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)","Divided government","Binding one-term limit","Binding two-term limit","Real per capita income ($1000)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues ($1000)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)"),
          add.lines = list(c("Effects","Pooled","Pooled","Fixed","Two-Way"))
          )
```

@@

\newpage

>>>>

```{r Barber summary statistics latex, results="asis", eval=TRUE}
# This is what fails to knit (see error below)
stargazer(as.data.frame(subset(BarberNAs[,3:6])), digits=0, type="latex", title="Descriptive Statistics for State Level Campaign Finance Limits (n=1150 state-years)", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"), header=F)
```

@@

```{r CRI summary latex, results="asis", eval=T}
stargazer(as.data.frame(subset(corruption[,c(3,6)])), type="latex", digits=2, title="Descriptive Statistics for Corruption and Reflections", covariate.labels = c("Corruption Convictions Index (CCI)","Corruption Reflections Index (CRI)"), header=F)

@@

The fourth data set provides controls for the panel model. In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization (see Appendix X). Alt and Lassen's data set runs from 1976-2004. When included in the second and third models, this limits the analysis to the years from 1990-2004.

@@

```{r Empty, Binomial, and Poisson models FAIL}
# First, trying to run the model above but with the pglm() package
# pglm(formula, data, subset, na.action, effect = c("individual", "time", "twoways"), model = c("random", "pooling", "within", "between"), family, other = NULL, index = NULL, start = NULL, R = 20, ...)

@@

@@
